ARuko and Editour: \\ A Platform for Augmented Reality Tour Guide Apps

### 2019-10-08 paper.tex

The field of consumer-oriented augmented reality (AR) technology is just coming
into full swing, and it presents many unique opportunities for a myriad of
fields. This budding technological platform uses digital displays to augment
real-world information with computer-generated data (see
Figure~\ref{fig:arExample}. As the technology progresses, several disparate
industries have found novel uses for it, some becoming extremely
profitable~\autocite{webster2018}. With smartphone manufacturers investing
billions into AR technology~\autocite{mason2016}, it seems poised to be the next
big digital interface.

@@

Tourism and art are among the fields that could gain the most from AR
technology~\autocite{saenz2009, katz2018}. This technology can provide
accessible information to tourists and art viewers that they would not be able
to get any other way. Kinkaku-ji, the ``Golden Pavilion'' of Kyoto (see
Figure~\ref{fig:kinkakuji1}, is the perfect example of a site that would benefit
from AR~\autocite{bornoff2000}.

@@

To solve this problem and open up the peerless beauty of the Golden Pavilion to
more people, our team created ARuko and Editour. These two tools comprise a
complete platform for designing and experiencing AR-enhanced tours. Editour
makes it easy to design custom audio tours including audio, text, and images,
while ARuko allows users to seamlessly experience historic sites in an intuitive
and novel way. Many AR apps require specific markers, like the those shown in
Figure~\ref{fig:arMarker}. To avoid the need to place any physical object that
would disturb the buildings or grounds of a historic site, our app does not rely
on these markers. Instead, ARuko recognizes images of objects that are already
at the site, and uses them to display informative AR pop-ups. See
Sections~\ref{sec:translationFeature} and \ref{sec:mapOverlayFeature} for more
details.

@@

As smartphones and mobile technology become more prevalent, new forms of
human-computer interaction are becoming mainstream. Smartphones allow for an
unprecedented degree of connectivity with the digital world, but can also serve
as a tool for digitally enhancing the physical world. In this section we explain
the origins and uses of this technology.

@@

For example, AR can be used to display information about historical events,
places, and objects overlaid onto images of the real
world~\autocite{saenz2009}, in a way that is more intuitive or visually
appealing than a purely virtual environment. This provides the user with useful
information without needing to alter the physical historic site.

@@

One of the major problems facing AR development as a whole---including our
project---is limited hardware. For starters, smartphone cameras present a
major limitation. Many smartphone cameras only capture images in 2D, which can
make generating AR content in a 3D world difficult without the use of QR or
barcode markers~\autocite{geospatialworld2018}. Additionally, GPS sensors on
smartphones can also be too imprecise for good AR
tracking~\autocite{geospatialworld2018}.

AR apps are most commonly designed for smartphones due to their relatively low
cost and how accessible they are. However, smartphones come with a host of
hardware limitations that make achieving satisfying AR capabilities difficult.
Additionally, AR apps for smartphones tend not to be very user-friendly, and
oftentimes even complicate the task or activity they were meant to
enhance~\autocite{theappsolutions2018}.  The alternative then is to turn to
dedicated hardware, like Microsoft's HoloLens. The issue is that dedicated
hardware like the HoloLens is very inaccessible and expensive; Microsoft only
offers developer editions of the HoloLens, and for the steep price of
\$3,500~\autocite{microsoft2019}.

@@

Wikitude is another major AR development kit that is very prevalent in the world
of AR development. It has over 130,000 registered AR developers, and is powering
over 30,000 AR apps across smartphones, tablets, and smart
glasses~\autocite{wikitude2018}. It is easy to understand why Wikitude has so
many registered developers considering the list of features the platform offers.
Some of the features that were most appealing to us were their ``Instant
Tracking,'' allowing for augmentation using flat surfaces; ``Image Tracking,''
allowing for augmentation using one or multiple 2D images; and ``Geo AR,''
allowing for creation of geo-markers at specific locations to trigger AR
content.

@@

Based on this information, Wikitude was initially appealing to us. However, the
cost was a major issue. Wikitude is free for eligible startups, but given the
criteria they list on their site, we were not confident that we would qualify.
Aside from this option, Wikitude offers a 30-day demo license for \euro{499},
which was far beyond the resources available to us. They also charge
\euro{1990} for their SDK Pro, and \euro{2490} for their SDK Pro 3D. Given
these prices, and our very limited budget, we decided to consider other
options.

@@

Unfortunately, it appears that the company has completely pivoted off of this
idea, and has since moved to developing AR training
software~\autocite{motiveio}. We reached out to motive.io via email for any
advice they might be willing to give us, but we received no response.

@@

Since our project is not a game, we initially wanted to avoid using a
fully-featured game engine such as Unity (see Section~\ref{sec:unity}.
Therefore, we decided to take the time to explore this framework since it
appeared to be more tailored to our specific use case. Viro Media also
recognizes that all developers who wish to create an app with 3D capabilities
are not necessarily game developers. Viro Media pitches ViroAR as ``The
perfect alternative to specialized game engines, ViroAR is a platform for
rapidly building ARKit and ARCore apps. Our platform allows developers to focus
on what they do best by leveraging familiar tools and frameworks used in mobile
application development''~\autocite{viro2019}. While the majority of our team
has decent experience with writing JavaScript, we have have very little
experience writing React apps.

@@

Since an emulator uses software to emulate hardware, this poses two technical
issues that prevent emulators from being a proper replacement for testing on
real hardware. Emulation is often imperfect, so glitches sometimes emerge in
emulation that do not manifest on the actual hardware~\autocite{alzaylaee2017}.
Conversely, errors that exist in the hardware version may not appear in the
emulation. Secondly, and most importantly for AR, it is common for emulation to
be much slower compared to real hardware.\footnote{In a question submitted to
\textit{Compute!} magazine asking whether it is possible for a Commodore 64 to
emulate MS-DOS, the editor responded ``Yes, it's possible for a 64 to emulate an
IBM PC, in the same sense that it's possible to bail out Lake Michigan with a
teaspoon.'' The editor goes on to explain ``Emulation is a complex business, but
here's one rule of thumb: The only way to successfully emulate a machine is with
a much more powerful machine''~\autocite{warick1988}. In our case, emulating
Android on a desktop operating system is closer to emulating a C64 on an IBM PC
running MS-DOS (rather than the other way around, thankfully). The takeaway is
that the speed problem facing emulators is just as real as it was in 1988.}
Considering that AR already pushes modern phone hardware to the limit, emulation
is not something we wanted to struggle with. On top of this, our testing
required us to move the camera through the world at various speeds and angles,
which is simply cumbersome with a laptop webcam.

@@

All of Unity's scripting is done with C\#, which is a general purpose,
object-oriented language~\autocite{ecmainternational2017}. Even though none of
us had extensive experience with C\# prior to this project, this was not of
great concern since C\# is similar to other object-oriented languages such as
Java and C++. The design goals of the language were also appealing to us; C\#
includes features important for programmer productivity such as strong type
checking (unlike JavaScript), detection of using uninitialized variables (also
unlike normal JavaScript,) range checking for array bounds (unlike C) and
garbage collection. At the same time, our lack of familiarity with the language
and Unity as a whole is another reason we first looked into cross-platform AR
solutions that did not use Unity.
%TODO see if we need more sources for this

@@

Unity is distinct from the technologies previously discussed in this section
because it is not an AR platform unto itself. Instead, Unity can take advantage
of AR platforms such as ARKit, ARCore, Vuforia and Wikitude through the use of
plugins.
%TODO provide citations that note that all of these platforms support Unity.

@@

An audio file and multiple image files can be uploaded for each region the user
defines. The user can also provide a text transcript of the audio file as well.
After naming and uploading the tour with the ``Upload'' button, our backend
builds a zip containing files that can be placed directly into the Unity
project.

@@

Even with knowledge of C\# and Unity, inputting tour data this way is obviously
cumbersome. Atticus is not a software developer, and does not want to work with
C\# scripts. In order to make our app prototype at all useful for the future,
we needed to provide an easy way to ``design'' a tour using a simple graphical
interface.

@@

In order to create a fully-functional editor for designing and exporting
``tours,'' we had to consider how to fully define a tour purely in terms
of text and a directory of associated media.

Here is an example of a tour metadata file in JavaScript Object Notation (JSON)
format:

@@

The user can easily create a new region by shift-clicking the map, and then
continuing to click to define more points. Figure~\ref{fig:drawingRegion} shows
this in action. To terminate the polygon, the user must shift-click again. The
``Welcome to Editour'' card (seen in Figure~\ref{fig:welcomeCard}) provides
these instructions, which should be enough to get started. A user can only
terminate the polygon after two points have been placed to prevent the user
from drawing a region with an area of zero. Once a region is created, a region
card appears in the side bar. From here, the user can edit anything about the
region.

@@

Once a tour is either uploaded or downloaded, a link to download the zip file of
that tour will appear. The zip file contains all of the uploaded media, and a
metadata file. The metadata is in the form of a JSON file; it contains all of
the latitudes, longitudes, and enough information to associate all of the media
with the correct regions. The downloaded zip file is what we decompress and
place into the Unity project before it is compiled. This feature is also useful
if the user wants to check the audio and image files that were uploaded.

@@

The frontend was implemented as a web application, using web technologies such
as HTML, CSS and JavaScript, with JavaScript being the vast majority of the
code. Type-checking provided by Visual Studio Code and JSDoc made the growing
code complexity more manageable.\footnote{One helpful specification of the
ECMAScript standard in the way of programmer sanity is ``strict mode.'' By
placing the string \texttt{"use strict"} at the top of a JavaScript source file,
errors will be thrown in many cases where ordinary JavaScript would not
complain. The simplest example of this is the line \texttt{a = 1;} will not
throw an error ordinarily. In strict mode, you must at first explicitly declare
the variable with the \texttt{let}, \texttt{var}, or \texttt{const} keyword
before assigning it, similar to Java or C++. We included the string at the
beginning of every source file except for class declarations, which are in
strict mode by default~\autocite[386]{ecmainternational2019}.} Excluding Node.js
modules, the only external library we used for Editour was Leaflet, which is
``an open-source JavaScript library for mobile-friendly interactive maps''
according to the official Leaflet website~\autocite{leafletjs}. We did not use
any framework for developing frontends like Facebook's React or Google's
Angular. Instead, all of the complex UI interactions were handled by modifying
the DOM directly with JavaScript's built-in functionality. Furthermore, we did
not use any advanced frontend build tools such as Rollup, webpack or Parcel. For
a JavaScript project of this scope, this was the correct decision. Considering
we had limited knowledge of React or Angular, it was also faster to develop the
UI in the way we were used to from previous experience, but if we were to
continue to develop Editour, UI libraries and frontend build tools would be
something to consider.

@@

The classes within CSS were designed so they could be reused
easily and composed with one another. If, for example, we needed to change the
font of every element that was styled like a button, we could do so by simply
changing the \texttt{font-family} attribute in a single CSS class. Consider the
green bar pictured in Figure~\ref{fig:mediaSubcard}. Multiple CSS classes were
composed in order to inherit the visual descriptions of other UI elements. The
four CSS classes on this bar are \texttt{button}, \texttt{greenbutton},
\texttt{outlinebutton}, and \texttt{revealer}. The class \texttt{button} styles
elements as the slightly raised, rounded rectangle that can be seen throughout
the UI. Additionally, all elements with the \texttt{button} class will have a
subtle ``press'' animation when being clicked on, since key frame animations can
also be defined in CSS. The default color of the button is red; the bottom of
the button is a slightly darker shade to give a 3D effect. Both of these colors
are conveniently stored as custom CSS variables, \texttt{--bg-color} and
\texttt{--bottom-color}. This allows another class to easily override these
colors. This is what the class \texttt{greenbutton} does; an HTML element with
the \texttt{button} class and either \texttt{greenbutton}, \texttt{orangebutton}
or \texttt{bluebutton} will be styled like a button and have a new color palette
applied. In order to differentiate the buttons that reveal subcards, the
\texttt{outlinebutton} class is used. This class takes the custom
\texttt{--bg-color} property and applies it to the border, drop shadow and text
color instead of the background. This class was also applied to the buttons that
can be seen in Figures~\ref{fig:jumpCard}~and~\ref{fig:downloadCard}. Finally,
the \texttt{revealer} class changes the text from centered to left-justified
among other minor formatting adjustments. CSS allowed us to define the look and
feel programmatically with the need to create graphical assets using image
editing software. This means that anyone using the codebase of Editour for
different purposes can easily change the look and feel of the frontend by
changing the CSS.\footnote{This is allowed since Editour is free software, which
is discussed briefly in Section~\ref{sec:futureOfEditour}.}

@@

When a user submits new tour from the web application, the files and metadata
are sent to the server running the Node.js scripts. The server zips up the files
and saves them to the disk with a time stamp. Then any application can request a
particular tour and the backend will serve the most recent version.

As previously mentioned in Section~\ref{sec:editingATour}, our web application
allows users to edit existing tours. When the user requests to edit a tour on
the frontend it sends a request to the backend server for that tour's metadata
file. This file contains information about all regions and files in the tour.
The user can then edit the regions, change names, upload new files, or delete
existing ones without ever having to download the other tour files from the
server, which could take a long time depending on their size. When the user is
done editing they can upload the new metadata and any newly added files to the
server, which intelligently collects new and old files required by the tour and
zips them into a new tour file on the disk.

@@

For testing and development purposes the Editour backend was originally hosted
on Joseph Petitti's personal server. This was a CentOS virtual machine running
on an old Dell rack server in Worcester, Massachusetts. We wrote a custom
systemd service to run Editour as a daemon and keep its log files organized. The
Node.js backend was served by an Nginx reverse proxy running on the same virtual
machine.

@@

Unfortunately, the hosting solution Kyoto~VR provided us with severely throttles
disk write speeds. Because the backend has to write potentially large amounts of
data to the disk every time a tour is uploaded or edited this becomes a major
bottleneck for the web app's performance. For large tours (bigger than 50 MiB)
this can cause an issue where the Node server takes so long to respond that
Apache thinks it has timed out, and sends an erroneous 504 Gateway Timeout
message~\autocite{rfc7231}. Without access to superuser permissions or a faster
hosting provider there is nothing we can do about this bug. The Node server does
eventually complete the request and respond correctly, so until Kyoto~VR can get
a better hosting provider we consider it a minor issue.

@@

The files produced by Editour could be used to power an app that does not
incorporate AR, such as an audio guide mobile web app that runs entirely in the
browser, using the geolocation API to access the user's location (if the user
grants permission). This kind of infrastructure would allow users to access an
audio tour---supplemented by images and audio transcripts---without the need to
download an app at all. By simply visiting a link, a user could experience a
guided tour that changes as the user walks through the route. For example,
colleges could distribute tour links via QR codes, which would instantly launch
an interactive guided tour of the campus through the browser.

Currently, anyone can clone the GitHub repository of Editour and deploy a
working version on a personal server. The source code for Editour is under a
free license, namely the GNU General Public License. This allows anyone to
expand the frontend and backend to suit their needs. With additional hardware
and by extending the current implementation of both the frontend and backend,
Editour could be used as the groundwork to create an entire crowd-sourced
walking tour platform, allowing users to design tours for others to take.

@@

The core user experience of ARuko is the walking tour. By walking the given
route, the user enters and exits specific geographic regions that invoke
changes in the app, such as playing audio and displaying different images.
Originally, we planned to mark regions by singular points, and trigger that
region if the user was within a certain radius of that point.
Implementation-wise, this would have been much simpler, but obviously limits
possible tour designs. Consequently, we decided at an early stage to
accommodate regions with arbitrary shape and size.  In the implementation, we
provided support for both ``GPS Bubbles'' and ``GPS Polygons.'' In the end
however, Editour made it trivial to use the more versatile ``GPS Polygons,'' so
we eventually dropped support for regions triggered by distance.
% TODO add a picture that shows how having only circular regions limits possible
% tour designs

@@

ARuko uses augmented reality to translate text at the site of the tour as well.
While AR translation apps exist, the experience can be frustrating, and produce
poor results. Google~Translate's text recognition and machine-learning powered
translation technology is certainly impressive. At the same time, the
translation service works better in ``scan'' mode instead of ``instant'' mode.
In ``instant'' mode, the app attempts to translate text as quickly as possible,
superimposing the translated text onto the real world using the camera. In
``scan'' mode, the user first takes a photo. This will sometimes produce
useless results, as seen in Figure~\ref{fig:translateInstant}. Then, the user
is prompted to highlight where text appears in the photo by dragging lines onto
the screen where text appears, as seen in Figure~\ref{fig:translateScan}. After
the translation is complete, the translated text appears in a separate UI
element, which can be seen in Figure~\ref{fig:translateFinalCard}. In most
cases, it is more convenient and readable to have the translation appear in a
separate scrollable text box. This motivated the current design of the ``info
buttons'' in ARuko. Instead of placing text directly onto signage, we place a
blue button with a stylized ``\textit{i}'' in the center. By tapping on this
button, a separate UI element will appear containing the translated text. Since
this button is cast into the world using the AR camera, the button appears to
be placed directly on top of the content.

@@

Additionally, we would not try to use any text recognition or translation APIs
to automate the translation. Figure~\ref{fig:translateInstant} demonstrates
that this kind of technology needs to mature before it is completely usable,
especially for Japanese. Instead, we had Atticus share a Google Sheets
spreadsheet. Hikaru Inoue manually translated each sign and provided notes about
his decision making process about each translation. Once this time-intensive
labor was completed, we took each field of translated text from the spreadsheet
and implemented it directly into the app, associating each translation with the
correct image target.

@@

Originally, the AR model of the Golden Pavilion was flush against the plane of
the ticket, sitting on the paper as if it were ground, as depicted in
Figure~\ref{fig:kinkakujiHorizontal}. Atticus suggested that we re-orient the
model such that the ticket served as a back plane, as pictured in
Figure~\ref{fig:souvenir}. This would allow users to hold the ticket vertically,
and view the Golden Pavilion floating in front of the ticket. This allows users
to place their hands under the base of the Golden Pavilion model as if they were
holding it; Vuforia's image tracking is flexible enough such that the image
target can be partially obscured by the hand.

@@

These tests were very useful in tracking down bugs and unexpected behavior in
the backend, and also allowed us to make sure no functionality changed when
adding new features or making changes to underlying logic later on.

@@

Additionally, one of the image targets had the wrong text in its information
pop-up. These were all easy bugs to fix, but if we might not have noticed
them if we had not tested the app on-site.

>>>>

Consumer-oriented augmented reality (AR) technology is just coming into full
swing, and it presents many unique opportunities for a myriad of fields. This
budding technological platform uses digital displays to augment real-world
information with computer-generated data (see Figure~\ref{fig:arExample}). As
the technology progresses, several disparate industries have found novel uses
for it, some becoming extremely profitable~\autocite{webster2018}. With
smartphone manufacturers investing billions into AR
technology~\autocite{mason2016}, it seems poised to be the next big digital
interface.

@@

Tourism and art are among the fields that could gain the most from AR
technology~\autocite{saenz2009, katz2018}. This technology can provide
accessible information to tourists and art viewers that they would not be able
to get any other way. Kinkaku-ji, the ``Golden Pavilion'' of Kyoto (see
Figure~\ref{fig:kinkakuji1}), is the perfect example of a site that would benefit
from AR~\autocite{bornoff2000}.

@@

To solve this problem and open up the peerless beauty of the Golden Pavilion to
more people, our team created ARuko and Editour. These two tools comprise a
complete platform for designing and experiencing AR-enhanced tours. Editour
makes it easy to design custom audio tours including sound, text, and images,
while ARuko allows users to seamlessly experience historic sites in an intuitive
and novel way. Many AR apps require specific markers, like the those shown in
Figure~\ref{fig:arMarker}. To avoid the need to place any physical object that
would disturb the buildings or grounds of a historic site, our app does not rely
on these markers. Instead, ARuko recognizes images of objects that are already
at the site and uses them to display informative AR pop-ups. See
Sections~\ref{sec:translationFeature} and \ref{sec:mapOverlayFeature} for more
details.

@@

As smartphones and mobile technology become more prevalent, new forms of
human-computer interaction are becoming mainstream. Smartphones allow for an
unprecedented degree of connectivity with the digital world but can also serve
as a tool for digitally enhancing the physical world. In this section we explain
the origins and uses of this technology.

@@

For example, AR can be used to display information about historical events,
places, and objects overlaid onto images of the real
world~\autocite{saenz2009} in a way that is more intuitive or visually
appealing than a purely virtual environment. This provides the user with useful
information without needing to alter the physical historic site.

@@

One of the major problems facing AR development as a whole---including our
project---is hardware. For starters, smartphone cameras present a
major limitation. Many smartphone cameras only capture images in 2D, which can
make generating AR content in a 3D world difficult without the use of QR or
barcode markers~\autocite{geospatialworld2018}. Additionally, GPS sensors on
smartphones can also be too imprecise for good AR
tracking~\autocite{geospatialworld2018}.

AR apps are most commonly designed for smartphones due to their relatively low
cost and how accessible they are. However, smartphones come with a host of
hardware limitations that make achieving satisfying AR capabilities difficult.
Additionally, AR apps for smartphones tend not to be very user-friendly and
oftentimes even complicate the task or activity they were meant to
enhance~\autocite{theappsolutions2018}.  The alternative then is to turn to
dedicated hardware, like Microsoft's HoloLens. The issue is that dedicated
hardware like the HoloLens is very inaccessible and expensive; Microsoft only
offers developer editions of the HoloLens and for the steep price of
\$3,500~\autocite{microsoft2019}.

@@

Wikitude is another major AR development kit that is very prevalent in the world
of AR development. It has over 130,000 registered AR developers and is powering
over 30,000 AR apps across smartphones, tablets, and smart
glasses~\autocite{wikitude2018}. It is easy to understand why Wikitude has so
many registered developers considering the list of features the platform offers.
Some of the features that were most appealing to us were their ``Instant
Tracking,'' allowing for augmentation using flat surfaces; ``Image Tracking,''
allowing for augmentation using one or multiple 2D images; and ``Geo AR,''
allowing for creation of geo-markers at specific locations to trigger AR
content.

@@

Based on this information, Wikitude was initially appealing to us. However, the
cost was a major issue. Wikitude is free for eligible startups, but given the
criteria they list on their site, we were not confident that we would qualify.
Aside from this option, Wikitude offers a 30-day demo license for \euro{499},
which was far beyond the resources available to us. They also charge
\euro{1990} for their SDK Pro and \euro{2490} for their SDK Pro 3D. Given
these prices, and our very limited budget, we decided to consider other
options.

@@

Unfortunately, it appears that the company has completely pivoted off of this
idea and has since moved to developing AR training software~\autocite{motiveio}.
We reached out to motive.io via email for any advice they might be willing to
give us, but we received no response.

@@

Since our project is not a game, we initially wanted to avoid using a
fully-featured game engine such as Unity (see Section~\ref{sec:unity}).
Therefore, we decided to take the time to explore this framework since it
appeared to be more tailored to our specific use case. Viro Media also
recognizes that all developers who wish to create an app with 3D capabilities
are not necessarily game developers. Viro Media pitches ViroAR as ``The
perfect alternative to specialized game engines, ViroAR is a platform for
rapidly building ARKit and ARCore apps. Our platform allows developers to focus
on what they do best by leveraging familiar tools and frameworks used in mobile
application development''~\autocite{viro2019}. While the majority of our team
has decent experience with writing JavaScript, we have have very little
experience writing React apps.

@@

Since an emulator uses software to emulate hardware, this poses two technical
issues that prevent emulators from being a proper replacement for testing on
real hardware. Emulation is often imperfect, so glitches sometimes emerge in
emulation that do not manifest on the actual hardware~\autocite{alzaylaee2017}.
Conversely, errors that exist in the hardware version may not appear in the
emulation. Secondly, and most importantly for AR, it is common for emulation to
be much slower compared to real hardware.\footnote{In a question submitted to
\textit{Compute!} magazine asking whether it is possible for a Commodore 64 to
emulate MS-DOS, the editor responded, ``Yes, it's possible for a 64 to emulate
an IBM PC, in the same sense that it's possible to bail out Lake Michigan with a
teaspoon.'' The editor goes on to explain, ``Emulation is a complex business,
but here's one rule of thumb: The only way to successfully emulate a machine is
with a much more powerful machine''~\autocite{warick1988}. In our case,
emulating Android on a desktop operating system is closer to emulating a C64 on
an IBM PC running MS-DOS (rather than the other way around, thankfully). The
takeaway is that the speed problem facing emulators is just as real as it was in
1988.} Considering that AR already pushes modern phone hardware to the limit,
emulation is not something we wanted to struggle with. On top of this, our
testing required us to move the camera through the world at various speeds and
angles, which is simply cumbersome with a laptop webcam.

@@

All of Unity's scripting is done with C\#, which is a general purpose,
object-oriented language~\autocite{ecmainternational2017}. Even though none of
us had extensive experience with C\# prior to this project, this was not of
great concern since C\# is similar to other object-oriented languages such as
Java and C++. The design goals of the language were also appealing to us; C\#
includes features important for programmer productivity such as strong type
checking (unlike JavaScript), detection of using uninitialized variables (also
unlike normal JavaScript) range checking for array bounds (unlike C), and
garbage collection. At the same time, our lack of familiarity with the language
and Unity as a whole is another reason we first looked into cross-platform AR
solutions that did not use Unity.
%TODO see if we need more sources for this

@@

Unity is distinct from the technologies previously discussed in this section
because it is not an AR platform unto itself. Instead, Unity can take advantage
of AR platforms such as ARKit, ARCore, Vuforia, and Wikitude through the use of
plugins.
%TODO provide citations that note that all of these platforms support Unity.

@@

An audio file and multiple image files can be uploaded for each region the user
defines. The user can also provide a text transcript of the audio file. After
naming and uploading the tour with the ``Upload'' button, our backend builds a
zip containing files that can be placed directly into the Unity project.

@@

Even with knowledge of C\# and Unity, inputting tour data this way is obviously
cumbersome. Atticus is not a software developer and does not want to work with
C\# scripts. In order to make our app prototype at all useful for the future,
we needed to provide an easy way to ``design'' a tour using a simple graphical
interface.

@@

In order to create a fully-functional editor for designing and exporting
``tours,'' we had to consider how to fully define a tour purely in terms of text
and a directory of associated media. Here is an example of a tour metadata file
in JavaScript Object Notation (JSON) format:

@@

The user can easily create a new region by shift-clicking the map and then
continuing to click to define more points. Figure~\ref{fig:drawingRegion} shows
this in action. To terminate the polygon, the user must shift-click again. The
``Welcome to Editour'' card (seen in Figure~\ref{fig:welcomeCard}) provides
these instructions, which should be enough to get started. A user can only
terminate the polygon with a third point after two points have already been
placed to prevent the user from drawing a region with an area of zero. Once a
region is created, a region card appears in the side bar. From here, the user
can edit anything about the region.

@@

Once a tour is either uploaded or downloaded, a link to download the zip file of
that tour will appear. The zip file contains all of the uploaded media and a
metadata file. The metadata is in the form of a JSON file; it contains all of
the latitudes, longitudes, and enough information to associate all of the media
with the correct regions. The downloaded zip file is what we decompress and
place into the Unity project before it is compiled. This feature is also useful
if the user wants to check the audio and image files that were uploaded.

@@

The frontend was implemented as a web application, using web technologies such
as HTML, CSS, and JavaScript, with JavaScript being the vast majority of the
code. Type-checking provided by Visual Studio Code and JSDoc made the growing
code complexity more manageable.\footnote{One helpful specification of the
ECMAScript standard in the way of programmer sanity is ``strict mode.'' By
placing the string \texttt{"use strict"} at the top of a JavaScript source file,
errors will be thrown in many cases where ordinary JavaScript would not
complain. The simplest example of this is the line \texttt{a = 1;} will not
throw an error ordinarily. In strict mode, you must at first explicitly declare
the variable with the \texttt{let}, \texttt{var}, or \texttt{const} keyword
before assigning it, similar to Java or C++. We included the string at the
beginning of every source file except for class declarations, which are in
strict mode by default~\autocite[386]{ecmainternational2019}.} Excluding Node.js
modules, the only external library we used for Editour was Leaflet, which is
``an open-source JavaScript library for mobile-friendly interactive maps''
according to the official Leaflet website~\autocite{leafletjs}. We did not use
any framework for developing frontends like Facebook's React or Google's
Angular. Instead, all of the complex UI interactions were handled by modifying
the DOM directly with JavaScript's built-in functionality. Furthermore, we did
not use any advanced frontend build tools such as Rollup, webpack, or Parcel.
For a JavaScript project of this scope, this was the correct decision.
Considering we had limited knowledge of React or Angular, it was also faster to
develop the UI in the way we were used to from previous experience, but if we
were to continue to develop Editour, UI libraries and frontend build tools would
be something to consider.

@@

The classes within CSS were designed so they could be reused easily and composed
with one another. If, for example, we needed to change the font of every element
that was styled like a button, we could do so by simply changing the
\texttt{font-family} attribute in a single CSS class. Consider the green bar
pictured in Figure~\ref{fig:mediaSubcard}. Multiple CSS classes were composed in
order to inherit the visual descriptions of other UI elements. The four CSS
classes on this bar are \texttt{button}, \texttt{greenbutton},
\texttt{outlinebutton}, and \texttt{revealer}. The class \texttt{button} styles
elements as the slightly raised, rounded rectangle that can be seen throughout
the UI. Additionally, all elements with the \texttt{button} class will have a
subtle ``press'' animation when being clicked on, since key frame animations can
also be defined in CSS. The default color of the button is red; the bottom of
the button is a slightly darker shade to give a 3D effect. Both of these colors
are conveniently stored as custom CSS variables, \texttt{--bg-color} and
\texttt{--bottom-color}. This allows another class to easily override these
colors. This is what the class \texttt{greenbutton} does; an HTML element with
the \texttt{button} class and either \texttt{greenbutton},
\texttt{orangebutton}, or \texttt{bluebutton} will be styled like a button and
have a new color palette applied. In order to differentiate the buttons that
reveal subcards, the \texttt{outlinebutton} class is used. This class takes the
custom \texttt{--bg-color} property and applies it to the border, drop shadow,
and text color instead of the background. This class was also applied to the
buttons that can be seen in
Figures~\ref{fig:jumpCard}~and~\ref{fig:downloadCard}. Finally, the
\texttt{revealer} class changes the text from centered to left-justified among
other minor formatting adjustments. CSS allowed us to define the look and feel
programmatically with the need to create graphical assets using image editing
software. This means that anyone using the codebase of Editour for different
purposes can easily change the look and feel of the frontend by changing the
CSS.\footnote{This is allowed since Editour is free software, which is discussed
briefly in Section~\ref{sec:futureOfEditour}.}

@@

When a user submits new tour from the web application, the files and metadata
are sent to the server running the Node.js scripts. The server zips up the files
and saves them to the disk with a time stamp. Then any application can request a
particular tour, and the backend will serve the most recent version.

As previously mentioned in Section~\ref{sec:editingATour}, our web application
allows users to edit existing tours. When the user requests to edit a tour on
the frontend, it sends a request to the backend server for that tour's metadata
file. This file contains information about all regions and files in the tour.
The user can then edit the regions, change names, upload new files, or delete
existing ones without ever having to download the other tour files from the
server, which could take a long time depending on their size. When the user is
done editing they can upload the new metadata and any newly added files to the
server, which intelligently collects new and old files required by the tour and
zips them into a new tour file on the disk.

@@

For testing and development purposes, Editour backend was originally hosted on
Joseph Petitti's personal server. This was a CentOS virtual machine running on
an old Dell rack server in Worcester, Massachusetts. We wrote a custom systemd
service to run Editour as a daemon and keep its log files organized. The Node.js
backend was served by an Nginx reverse proxy running on the same virtual
machine.

@@

Unfortunately, the hosting solution Kyoto~VR provided us with severely throttles
disk write speeds. Because the backend has to write potentially large amounts of
data to the disk every time a tour is uploaded or edited this becomes a major
bottleneck for the web app's performance. For large tours (bigger than 50 MiB)
this can cause an issue where the Node server takes so long to respond that
Apache thinks it has timed out and sends an erroneous 504 Gateway Timeout
message~\autocite{rfc7231}. Without access to superuser permissions or a faster
hosting provider there is nothing we can do about this bug. The Node server does
eventually complete the request and respond correctly, so until Kyoto~VR can get
a better hosting provider we consider it a minor issue.

@@

The files produced by Editour could be used to power an app that does not
incorporate AR, such as an audio guide mobile web app that runs entirely in the
browser, and uses the geolocation API to access the user's location (if the user
grants permission). This kind of infrastructure would allow users to access an
audio tour---supplemented by images and audio transcripts---without the need to
download an app at all. By simply visiting a link, a user could experience a
guided tour that changes as the user walks through the route. For example,
colleges could distribute tour links via QR codes, which would instantly launch
an interactive guided tour of the campus through the browser.

Currently, anyone can clone the GitHub repository of Editour and deploy a
working version on a personal server. The source code for Editour is under the
GNU General Public License. This is a free license that allows anyone to expand
the frontend and backend to suit their needs. With additional hardware and by
extending the current implementation of both the frontend and backend, Editour
could be used as the groundwork to create an entire crowd-sourced walking tour
platform, allowing users to design tours for others to take.

@@

The core user experience of ARuko is the walking tour. By walking the given
route, the user enters and exits specific geographic regions that invoke changes
in the app, such as playing audio and displaying different images. Originally,
we planned to mark regions by singular points and trigger that region if the
user was within a certain radius of that point. Implementation-wise, this would
have been much simpler but obviously limits possible tour designs.
Consequently, we decided at an early stage to accommodate regions with arbitrary
shape and size.  In the implementation, we provided support for both ``GPS
Bubbles'' and ``GPS Polygons.'' In the end however, Editour made it trivial to
use the more versatile ``GPS Polygons,'' so we eventually dropped support for
regions triggered by distance.
% TODO add a picture that shows how having only circular regions limits possible
% tour designs

@@

ARuko uses augmented reality to translate text at the site of the tour as well.
While AR translation apps exist, the experience can be frustrating and can
produce poor results. Google~Translate's text recognition and machine-learning
powered translation technology is certainly impressive. At the same time, the
translation service works better in ``scan'' mode instead of ``instant'' mode.
In ``instant'' mode, the app attempts to translate text as quickly as possible,
superimposing the translated text onto the real world using the camera. In
``scan'' mode, the user first takes a photo. This will sometimes produce useless
results, as seen in Figure~\ref{fig:translateInstant}. Then, the user is
prompted to highlight where text appears in the photo by dragging lines onto the
screen where text appears, as seen in Figure~\ref{fig:translateScan}. After the
translation is complete, the translated text appears in a separate UI element,
which can be seen in Figure~\ref{fig:translateFinalCard}. In most cases, it is
more convenient and readable to have the translation appear in a separate
scrollable text box. This motivated the current design of the ``info buttons''
in ARuko. Instead of placing text directly onto signage, we place a blue button
with a stylized ``\textit{i}'' in the center. By tapping on this button, a
separate UI element will appear containing the translated text. Since this
button is cast into the world using the AR camera, the button appears to be
placed directly on top of the content.

@@

Additionally, we would not try to use any text recognition or translation APIs
to automate the translation. Figure~\ref{fig:translateInstant} demonstrates
that this kind of technology needs to mature before it is completely usable,
especially for Japanese. Instead, we had Atticus share a Google Sheets
spreadsheet. Hikaru Inoue manually translated each sign and provided notes about
his decision-making process about each translation. Once this time-intensive
labor was completed, we took each field of translated text from the spreadsheet
and implemented it directly into the app, associating each translation with the
correct image target.

@@

Originally, the AR model of the Golden Pavilion was flush against the plane of
the ticket, sitting on the paper as if it were ground, as depicted in
Figure~\ref{fig:kinkakujiHorizontal}. Atticus suggested that we re-orient the
model such that the ticket served as a back plane, as pictured in
Figure~\ref{fig:souvenir}. This would allow users to hold the ticket vertically
and view the Golden Pavilion floating in front of the ticket. This allows users
to place their hands under the base of the Golden Pavilion model as if they were
holding it; Vuforia's image tracking is flexible enough such that the image
target can be partially obscured by the hand.

@@

These tests were very useful in tracking down bugs and unexpected behavior in
the backend, and they also allowed us to make sure no functionality changed when
adding new features or making changes to underlying logic later on.

@@

Additionally, one of the image targets had the wrong text in its information
pop-up. These were all easy bugs to fix, but we might not have noticed them if
we had not tested the app on-site.
